---
title: "Explore Triangle Plots"
author: "Ben Wiens"
date: "4/4/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

# Punnet Squares

# Hardy-Weinbergy Equilibrium

# Try it out

Show possible space on triangle plot under HWE
Explain why this is the case mathematically
Shiny app: input HI and HET of 2 parents, output offspring HI and HET on plot

Example with simulated data:
1. See distribution of allele frequency differences
2. Get names of AIMs
3. Try multiple thresholds and get vcfRs
4. Calculate HI and HET
5. Compare triangle plots

Shiny app: choose number of parental samples, d, and number of SNPs that pass (downsample), build triangle plot

Example with real data:
1. See distribution of allele frequency differences
2. Try multiple thresholds and get vcfRs
3. Calculate HI and HET
4. Compare triangle plots
5. Color by missing data

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



</style>

<div class="shiny-app-frame"> 
<iframe src="https://omys-omics.shinyapps.io/Hybrid_Offspring/" width="500" height="1000">
</iframe>
</div>
